The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-20 analysis/paper/paper.qmd

emu_theses_top_20 %>%
  slice(1:40) %>% 
  ggplot(aes(x = reorder(word, n), y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2)

# # wip function ngrams
# get_ngrams <- function(df, n) {
#   if (!is.numeric(n)) {
#     stop("n is not numeric")
#   }
#   emu_theses %>%
#     mutate(author = paste(first_name, last_name)) %>% 
#     select(author, title, text, -c(year, first_name, last_name, text_start, text_end)) %>% 
#     unnest_tokens(bigram, text, token = "ngrams", n = 2) %>% 
#     separate(bigram, into = c("first","second"), sep = " ", remove = FALSE) %>%
#     anti_join(stop_words, by = c("first" = "word")) %>%
#     anti_join(stop_words, by = c("second" = "word")) %>%
#     anti_join(stop_words_custom, by = c("first" = "word")) %>%
#     anti_join(stop_words_custom, by = c("second" = "word")) %>%
#     filter(str_detect(first, "[a-z]") & str_detect(second, "[a-z]")) %>% 
#     filter(first != second) %>% 
#     filter(first != "source")
# }
# emu_theses_ngrams <- get_ngrams(emu_theses, 2)

# bigrams
emu_theses_bigrams <- emu_theses %>%
  mutate(author = paste(first_name, last_name)) %>% 
  select(author, title, text, -c(graduation_year, first_name, last_name)) %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>% 
  separate(bigram, into = c("first","second"), sep = " ", remove = FALSE) %>%
  anti_join(stop_words, by = c("first" = "word")) %>%
  anti_join(stop_words, by = c("second" = "word")) %>%
  anti_join(stop_words_custom, by = c("first" = "word")) %>%
  anti_join(stop_words_custom, by = c("second" = "word")) %>%
  filter(str_detect(first, "[a-z]") & str_detect(second, "[a-z]")) %>% 
  filter(first != second) %>% 
  filter(first != "source")

emu_theses_bigrams_top <- emu_theses_bigrams %>%
  group_by(title) %>%
  count(bigram, sort = TRUE) %>%
  slice_max(n, n = 10) %>%        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  ungroup() %>% 
  mutate(bigram = reorder(bigram, n))

>>>>

emu_theses_top_20 %>%
  slice(1:40) %>% 
  ggplot(aes(x = reorder(word, n), y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2)
```

```{r}
#| label: ngrams

## TO DO: generalise bigrams and trigrams into ngrams function

## Bigrams
emu_theses_bigrams <- emu_theses |> 
  unnest_tokens(bigram, text, token = "ngrams", n = 2) |> 
  separate(bigram, into = c("first", "second"), sep = " ", remove = FALSE) |> 
  anti_join(stop_words, by = c("first" = "word")) |> 
  anti_join(stop_words, by = c("second" = "word")) |> 
  filter(str_detect(first, "[a-z]") & 
         str_detect(second, "[a-z]"))

bigram_counts <- emu_theses_bigrams |> 
  count(first, second, sort = TRUE)

bigram_counts

## Trigrams
emu_theses_trigrams <- emu_theses |> 
  unnest_tokens(trigram, text, token = "ngrams", n = 3) |> 
  separate(trigram, into = c("first", "second", "third"), sep = " ", remove = FALSE) |> 
  filter(!first %in% stop_words$word,
         !second %in% stop_words$word,
         !third %in% stop_words$word) |>  
  filter(str_detect(first, "[a-z]"), 
         str_detect(second, "[a-z]"),
         str_detect(third, "[a-z]"))

trigram_counts <- emu_theses_trigrams |> 
  count(first, second, sort = TRUE)

trigram_counts

## Bigram tf-idf
bigram_tf_idf <- emu_theses_bigrams |> 
  count(title, bigram) |> 
  bind_tf_idf(bigram, title, n) |> 
  arrange(desc(tf_idf))

bigram_tf_idf

## Trigram tf-idf
trigram_tf_idf <- emu_theses_trigrams |> 
  count(title, trigram) |> 
  bind_tf_idf(trigram, title, n) |> 
  arrange(desc(tf_idf))

trigram_tf_idf

## Show network of bigrams
bigram_graph <- bigram_counts |> 
  filter(n > 100) |> 
  graph_from_data_frame()

bigram_graph

set.seed(2023)

a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()

## Higgh frequency bigrams ----

emu_theses_bigrams_top <- emu_theses_bigrams %>%
  group_by(title) %>%
  count(bigram, sort = TRUE) %>%
  slice_max(n, n = 20) %>%        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  ungroup() %>% 
  mutate(bigram = reorder(bigram, n))
